Fake Clicks on Video Ads

### 2015-05-05 doc/paper.tex
fix latex bug
update latex

\usepackage{graphicx}
\usepackage{caption}
\usepackage{listings}   %% for code syntax
\lstset{breaklines=true, breakatwhitespace=true}
\lstset{basicstyle=\small}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{abstract}
Keeping accurate account of views on video advertisement is important since it is now being treated as currency~\cite{c17}. In ``pay per click'' arrangement, publisher (owner of a website), hosts an advertisement and receives pay based on how many users view/click on the advertisement~\cite{c17, c18, c19}. The advertisement is provided by the advertiser (business owner) who pays the publishers so that their advertisement can be viewed by users who visit the website owned by the publisher. This has created an incentive for hackers to generate cheap artificial views on advertisement and trick advertisers to pay significant amount of money~\cite{c17, c18}. In this paper, we analyze traffic of fake views generated by hackers on YouTube and Dailymotion videos. Then we tested various in-house automated programs which mimic the characteristics of traffic generated by the hackers and see if YouTube will accept it as legitimate view.
\end{abstract}

@@

In this paper, we used 4 services that claim to generate view counts on videos hosted by YouTube and Dailymotion. The prices of their services ranged from 3 to 300 dollars and offered view counts from 50 to 50,000. We purchased the cheapest service ranging from 3 to 8 dollars for 500 to 5000 views. All four services were able to deliver their view counts in span of 2 to 7 days. The statistical data from YouTube and Dailymotion were limited; however, we did find some interesting data as well as verify some information that were stated in other research papers about fake views. Lastly, we wrote some programs which mimics the characteristics of traffics that were analyzed from services that generates view counts for monetary payment. Our programs were tested on videos hosted in YouTube.

@@

Aside from the view counts, this service also offered to generate comments on YouTube video. This website claims to offer 24/7 customer support via emails and also chat services. The chat services didn’t seems to work as no one replied when we started to use their chat service screen. Moreover, when we sent an email asking about their basic operation on March 2, 2015, we didn’t receive any reply as of April 16, 2015. However, when we purchase their service of 1000 views for 3 dollars, we did receive a confirmation email from socialwarehouseorg@gmail.com with the name ``Kevin M''.

@@

The Dalisocial site did not offer granular services like buildmyviews.org. For example, it just offered one option to purchase 5000 YouTube views for 7 dollars within 3 days. We noticed the most of the link on the site didn’t work. For example, nothing happened when we clicked the ``Contact Us'', ``About Us'', and ``Blog'' link. The . y link that worked was the ``Login'' which directs to a page to purchase services. We did receive an email when we registered and purchase their service of 5000 views for 7 dollars. The email was from noreply@dalisocial.com.

@@

We used this service to gene. e 2000 views for 7.5 dollars on video hosted by YouTube as well as 500 views for 5 dollars. video that is hosted on Dailymotion.com. And of course, we did received a confirmation order email with tracking numbers. The most surprising about this site is that they admit that they are generating fake clicks, views, and followers. This is depicted on their “About” page and the screen shot displayed in Figure 3 below.

@@

The last service that we used was from http://www.scopecompany.com. The IP address of this website is 209.59.134.1, hosted by Liquid Web. located in Lansing, U.S. Based on the site, the company states that they are located in New York, US; Mansoura, Egypt; as well as Tokyo, Japan. Aside from generating views on social websites, they offer web solutions such as web design and development to include specific graphic services.
We used this service to generate 1000 views for 8 dollars on video that is hosted on Dailymotion.com. We did receive a confirmation order email with a tracking number. However, it has been over a week but yet to see any view counts generated on our target video. We have sent an email acquiring the status of our order but have not receive any replied since April 15, 2015. The website states they 100\% safe and will always deliver within 1 to 5 days.

@@

\begin{figure}
  \centering
  \includegraphics[width=3.0in]{fig5a}
  \caption{Map representation of view source}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=3.0in]{fig5b}
  \caption{The top 5 countries}
\end{figure}

@@

\begin{enumerate}
  \item The largest chunk of views have been received from Russia (26\%) followed by Argentina (6.4\%), Indonesia (5.4\%), then India (4.7\%).
  \item Average view duration is between 41 to 43 seconds.
  \item There were many ways to view videos on YouTube to include advertised suggested links and through other host sites. All of the views generated by the bots are from ``YouTube watchpage'' that is, by typing the URL address or clicking on a link that leads directly to the video on YouTube.
  \item All views used Blackberry OS.
\end{enumerate}

@@

\begin{enumerate}
  \item The services is using same type of bot given the view length time was constant between 41 to 43 seconds, all used Blackberry, and same access method.
  \item The bots are most present in Russia as it showed the most view sources. We are assuming the IP was not spoofed as it is very difficult.
  \item Bots viewed the video for constant duration. This could help us distinguish between the legitimate views from bot generated views.
  \item Bots from buildmyviews.org can only view videos by directly accessing the URL link. The bots are not sophisticated enough to vary their viewing methods such as using advertised links.
  \item might be large amount of comprised Blackberry devices around the world; however, the bots might be modifying the traffic to disguise their real operating system.
\end{enumerate}

@@

\begin{figure}
  \centering
  \includegraphics[width=3.0in]{fig6a}
  \caption{Map representation of view source}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=3.0in]{fig6b}
  \caption{The top 5 countries}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=3.0in]{fig7a}
  \caption{\label{7a} Map representation of view source}

\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=3.0in]{fig7b}
  \caption{The top 5 countries}
\end{figure}

@@

\begin{enumerate}
  \item Dalisocial.com used different type of bot than Buildmyviews.org and SocialWarrior.net, as it showed different characteristics:
  \begin{itemize}
    \item Different source concentration, Middle East vs. Russia
    \item 2 different access methods vs. 1 access method
    \item Various OS vs. one Blackberry OS
  \end{itemize}
  \item Bots used by Dalisocial.com were more sophisticated as the traffics seem like a real users. They were able to access the video in different ways, view the whole length, and used various different devices/OS.
  \item The bots used by Dalisocial.com are most concentrated on Middle East as top 5 sources are from that area.
  \item The bots somehow made Google accounts to access the video via link suggested by YouTube homepage. This type of access is only available with having a Google account, thus it shows the high sophistication level of these bots. There is also a possibility that Dalisocial.com used a real users to generate the views; however, it is highly unlikely that they are connected with hundreds of users over 20 different countries who would offer this type of services for \$7.
\end{enumerate}

@@

\begin{enumerate}
  \item Not all traffics from the bots are counted as views. Which means, there is no definite way for the services to provide the exact number of views as required by the customers. It was found all 3 services overprovided the number of views requested. This implies that there is a central command system which turns the bots on to generate the traffic, then turns them off when the view counts are roughly met.
  \item There are at least 2 different type of bots used to generate artificial view counts. This is obvious as Dalisocial.com used different bots than the other two services. We assume that Buildmyviews.org and SocialWarrior.net used the same type of bot since the characteristics were very similar as well as services offered by the two websites.
  \item There is a possibility that many Blackberry devices are infected with bots that are being used to generate artificial view counts. According to PMR, there are at least 100,000 Blackberry devices in Russia since 2011~\cite{c13}, which bot type of malware was discovered on mobile devices, including Blackberry, around the same time\~cite{c12}.
  \item The businesses which offer to generate view counts on social media sites are not professionally maintained. One of the services did not deliver the view counts after taking the payment from our pre-paid credit card account. Moreover, all 4 services did not reply to our calls and emails that were provided on their customer care site.
\end{enumerate}

@@

Here we explain the interaction between the client browser and videos hosted in YouTube. This understanding is necessary as we used this mechanism to write the code to generate fake views on YouTube.

\begin{enumerate}
  \item When client browser tries to view a video from YouTube, it sends HTTP GET Request to YouTube service, then loads the following HTML code to create a blank video player:
  \begin{lstlisting}[frame=single, language=html]
<div id="player-api" class="player-width player-height off-screen-target player-api" tabIndex="-1">
</div>
  \end{lstlisting}
  \item YouTube sends Javascript Code which loads the YouTube player (Adobe Flash Player) into the client’s browser
  \begin{lstlisting}[frame=single, language=html]
<script>
var ytplayer = ytplayer || {};
ytplayer.config = { "min_version":"8.0.0", "url":"https:.../watch_as3.swf"
…
</script>
  \end{lstlisting}
  \item Lastly, the YouTube sends necessary data to the browser so the YouTube video player can load the specific video the browser requested. Then the video is played automatically and at this point, it should generated a view count.
  \begin{lstlisting}[frame=single, language=html]
<embed name="movie_player" id="movie\_player" type="application/x-shockwave-flash" src="https:.../watch\_as3.swf" allowscriptaccess="always" bgcolor="#000000" allowfullscreen="true" ...>
  \end{lstlisting}
\end{enumerate}

@@

The following is the basic steps of our scripts to generate views on videos hosted in YouTube:

@@

Refer to the appendix for the actual code. With our code, we were able to generate at least 301 view counts on videos hosted in YouTube, using one machine with one browser agent. This is because YouTube view counting system analyzes the view counts after 300 and determined that the views generated by our code isn’t from a real user. In our next section, we explain how we used our code in various ways to implement more unique IP addresses, user agents, proxy, and VPN connections to generate break the 301 views on videos hosted in YouTube.

@@

We modified our code to use a specific user agent string or parse it from a file that has a list of different user agent strings. Please refer to the appendix for full description of different parameters that could be used.

@@

Setup environment where this experiment was executed:
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item OS: Ubuntu 14.01 Server
  \item Duration: From April 28$^{th}$ 2030~2300 (2hr, 30min)
  \item Public IP: 172.31.20.23
  \item User agent: 526 different user agents
  \item 150~200 views every hour
\end{itemize}

subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count quickly generated to 301 in few hours but unchanged as of May 3rd, 2015.
  \item User agent information can easily be changed, thus there is probably no mechanism to verify if user agent string actually matches the source OS/browser used.
  \item For user agents with BlackBerry strings, YouTube sent pure HTML files with link to RTSP stream protocol instead of adobe flash player.
\end{itemize}

@@

Here we used multiple public IP addresses with our code to pass the 301 view threshold on video hosted in YouTube. Considering only IPv4, there are little less than 4 billion public IP addresses available in the world.

@@

subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count quickly generated to 301 within one hour but unchanged as of May 4$^{th}$ 2015.
  \item 5 public IP addresses isn’t enough to pass 301 view count.
\end{itemize}

@@

The Onion Router provides user anonymity on the Internet through encryption and using 3 random node connections between the source and the destination.

We thought about using TOR because it can incorporate many public IP addresses using different TOR exit nodes with our code. If the TOR daemon is configured to setup a new circuit every time our code views a YouTube video, we can use hundreds of different IP addresses since there are around 1000 different exit nodes available.

@@

subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count is still stuck at 301.
  \item Source IP is visible via flash browser plugin
  \item Anonymity isn’t possible using TOR when viewing videos in YouTube.
\end{itemize}

@@

Virtual Private Network is a connection that extends to another network through public network connection. Many higher institutions offer VPN service so students and staff can connect to the institution’s network from home or other geographic locations.

There are many public VPN connections available and we wanted to test our Code using VPN connections to see if this will break the 301 view count on YouTube videos.

@@

subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count is still stuck at 301.
  \item Using popular VPN connection doesn’t matter.
\end{itemize}

@@

We were able to generate 301 view count on video using our code in various different ways. However, we were not able to pass the 301 view count as of May 4$^{th}$ 2015. We also like to mention that we used combination of our experiments on one video hosted by YouTube. For example, we used VPN connection and 5 Cloud instances using multiple user agents. The result was similar as we were able to generate view count up to 301 views but no more.

Lastly, YouTube counting system isn’t perfect as it proven to allow both false positive and false negative view counts in our research. We were able to prove it allows false positive view counts by using the 4 services mentioned in section 2 \& 3. Moreover, for the videos that were stuck on 301+ views, we view the same videos manually and see if the view count will go over 301. The view counts didn’t change even after we manually view the videos; therefore, we assume that YouTube’s counting
system is also proven to false negative view counts.

>>>>

\usepackage{graphicx}
\usepackage{caption}
\usepackage{listings}   %% for code syntax
\lstset{breaklines=true, breakatwhitespace=true}
\lstset{basicstyle=\sffamily}
\lstset{basicstyle=\scriptsize}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{abstract}
Keeping accurate account of views on video advertisement is important since it is now being treated as currency~\cite{c17}. In ``pay per click'' arrangement, publisher (owner of a website), hosts an advertisement and receives pay based on how many users view/click on the advertisement~\cite{c17, c18, c19}. The advertisement is provided by the advertiser (business owner) who pays the publishers so that their advertisement can be viewed by users who visit the website owned by the publisher. This has created an incentive for hackers to generate cheap artificial views on advertisement and trick advertisers to pay significant amount of money~\cite{c17, c18}. In this paper, we analyze traffic of fake views generated by hackers on YouTube and Dailymotion videos. Then we wrote a code which was experimented in various ways to mimic the characteristics of traffic generated by the bots and see if YouTube will accept it as legitimate view
\end{abstract}

@@

In this paper, we used 4 services that claim to generate view counts on videos hosted by YouTube and Dailymotion. The prices of their services ranged from 3 to 300 dollars and offered view counts from 50 to 50,000. We purchased the cheapest service ranging from 3 to 8 dollars for 500 to 5000 views. Only three services were able to deliver their view counts in span of 2 to 7 days while one service still haven’t deliver as of May 4$^{th}$ 2015. The statistical data from YouTube and Dailymotion were limited; however, we did find some interesting data as well as verify some information that were stated in other research papers about fake views. Lastly, we wrote some programs which mimics the characteristics of traffics that were analyzed from services that generates view counts for monetary payment. Our programs were tested on videos hosted in YouTube.

@@

Aside from the view counts, this service also offered to generate comments on YouTube video. This website claims to offer 24/7 customer support via emails and also chat services. The chat services didn’t seems to work as no one replied when we started to use their chat service screen. Moreover, when we sent an email asking about their basic operation on March 2, 2015, we didn’t receive any reply as of April 2$^{nd}$, 2015. However, when we purchase their service of 1000 views for 3 dollars, we did receive a confirmation email from socialwarehouseorg@gmail.com with the name ``Kevin M''.

@@

The Dalisocial site did not offer granular services like buildmyviews.org. For example, it just offered one option to purchase 5000 YouTube views for 7 dollars within 3 days. We noticed the most of the link on the site didn’t work. For example, nothing happened when we clicked the ``Contact Us'', ``About Us'', and ``Blog'' link. The only link that worked was the ``Login'' which directs to a page to purchase services. We did receive an email when we registered and purchase their service of 5000 views for 7 dollars. The email was from noreply@dalisocial.com.

@@

We used this service to generate 2000 views for 7.5 dollars on video hosted by YouTube as well as 500 views for 5 dollars on a video that is hosted by DailyMotion.com. And of course, we did received a confirmation order email with tracking number. The most surprising about this site is that they admit that they are generating fake clicks, views, and followers. This is depicted on their ``About'' page and the screen shot displayed in Figure 3 below.

@@

The last service that we used was from http://www.scopecompany.com. The IP address of this website is 209.59.134.1, hosted by Liquid Web. located in Lansing, U.S. Based on the site, the company states that they are located in New York, US; Mansoura, Egypt; as well as Tokyo, Japan. Aside from generating views on social websites, they offer web service solutions such as web design and development to include specific graphic services.
We used this service to generate 1000 views for 8 dollars on video that is hosted on Dailymotion.com. We did receive a confirmation order email with a tracking number. However, we are yet to see any view counts generated on our target video. We have sent an email acquiring the status of our order but have not receive any reply since May 4$^{th}$, 2015. The website states they 100\% safe and will always deliver within 1 to 5 days.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in]{fig5a}
  \caption{Map representation of view source}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in]{fig5b}
  \caption{The top 5 countries}
\end{figure}

@@

\begin{enumerate}
  \item The largest chunk of views have been received from Russia (26\%) followed by Argentina (6.4\%), Indonesia (5.4\%), then India (4.7\%).
  \item Average view duration is between 41 to 43 seconds.
  \item There were many ways to view videos on YouTube to include advertised suggested links and through other host sites~\cite{c20}. All of the views generated by the bots are from ``YouTube watchpage'' that is, by typing the URL address or clicking on a link that leads directly to the video on YouTube.
  \item All views used Blackberry OS.
\end{enumerate}

@@

\begin{enumerate}
  \item The services is using same type of bot given the view length time was constant between 41 to 43 seconds, all used Blackberry, and same access method.
  \item The bots are most present in Russia as it showed the most view sources. We are assuming the IP was not spoofed as it is very difficult.
  \item Bots viewed the video for constant duration. This could help us distinguish between the legitimate views from bot generated views.
  \item Bots from buildmyviews.org can only view videos by directly accessing the URL link. The bots are not sophisticated enough to vary their viewing methods such as using advertised links.
  \item might be large amount of comprised Blackberry devices around the world~\cite{c12, c13}; however, the bots might be modifying the traffic to disguise their real operating system.
\end{enumerate}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in]{fig6a}
  \caption{Map representation of view source}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in]{fig6b}
  \caption{The top 5 countries}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in]{fig7a}
  \caption{\label{7a} Map representation of view source}

\end{figure}
\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in]{fig7b}
  \caption{The top 5 countries}
\end{figure}

@@

\begin{enumerate}
  \item Dalisocial.com used different type of bot than Buildmyviews.org and SocialWarrior.net, as it showed different characteristics:
  \begin{itemize}
    \item Different source concentration, Middle East vs. Russia
    \item 2 different access methods vs. 1 access method
    \item Various OS vs. one Blackberry OS
  \end{itemize}
  \item Bots used by Dalisocial.com were more sophisticated as the traffics seem like a real users. They were able to access the video in different ways, view the whole length, and used various different devices/OS.
  \item The bots used by Dalisocial.com are most concentrated on Middle East as top 5 sources are from that area.
  \item The bots somehow made Google accounts to access the video via link suggested by YouTube homepage. This type of access is only available with having a Google account, thus it shows the high sophistication level of these bots~\cite{c21}. There is also a possibility that Dalisocial.com used a real users to generate the views; however, it is highly unlikely that they are connected with hundreds of users over 20 different countries who would collaborate to provide this type of services for \$7.
\end{enumerate}

@@

\begin{enumerate}
  \item Not all traffics from the bots are counted as views. Which means, there is no definite way for the services to provide the exact number of views as required by the customers. It was found all 3 services overprovided the number of views requested. This implies that there is a central command system which turns the bots on to generate the traffic, then turns them off when the view counts are roughly met.
  \item There are at least 2 different type of bots used to generate artificial view counts. This is obvious as Dalisocial.com used different bots than the other two services. We assume that Buildmyviews.org and SocialWarrior.net used the same type of bot since the characteristics were very similar as well as services offered by the two websites.
  \item There is a possibility that many Blackberry devices are infected with bots that are being used to generate artificial view counts. According to PMR, there are at least 100,000 Blackberry devices in Russia since 2011~\cite{c13}, which bot type of malware was discovered on mobile devices, including Blackberry, around the same time~\cite{c12}.
  \item The businesses which offer to generate view counts on social media sites are not professionally maintained. One of the services did not deliver the view counts after taking the payment from our pre-paid credit card account. Moreover, all 4 services did not reply to our calls and emails that were provided on their customer care site.
\end{enumerate}

@@

Here we explain the interaction between the client browser and videos hosted in YouTube. We learned the interaction by observing the source HTML code on our browser when loading videos on YouTube. This understanding is necessary as we used this mechanism to write the code to generate fake views on YouTube.

\begin{enumerate}
  \item When client browser tries to view a video from YouTube, it sends HTTP GET Request to YouTube service, then loads the following HTML code to create a blank video player:
  \begin{lstlisting}[frame=single, language=html]
<div id="player-api" class="player-width player-height off-screen-target player-api" tabIndex="-1">
</div>
  \end{lstlisting}
  \item The JavaScript code within the HTML file loads the YouTube player (Adobe Flash Player) into the client’s browser.
  \begin{lstlisting}[frame=single, language=html]
<script>
  var ytplayer = ytplayer || {};
  ytplayer.config = { "min_version":"8.0.0", "url":"https:.../watch_as3.swf"
  ...
</script>
  \end{lstlisting}
  \item Lastly, the YouTube sends necessary data to the browser so the YouTube video player can load the specific video the browser requested. Then the video is played automatically and at this point, it should generated a view count.
  \begin{lstlisting}[frame=single, language=html]
<embed name="movie_player" id="movie\_player" type="application/x-shockwave-flash" src="https:.../watch\_as3.swf" allowscriptaccess="always" bgcolor="#000000" allowfullscreen="true" ...>
  \end{lstlisting}
\end{enumerate}

@@

The following are the steps of execution of our code to generate views on videos hosted in YouTube:

@@

Refer to our Github repository for the actual code (https://github.com/heronyang/youtube\_fake\_view). With our code, we were able to generate at least 301 view counts on videos hosted in YouTube, using one machine with one user agent. This is because YouTube view counting system analyzes the view counts after 301 and determined that the views generated by our code isn’t from a real user. In our next section, we explain how we used our code in various ways to implement more unique IP addresses, user agents, and VPN connections to pass the 301 views on videos hosted in YouTube.

@@

We modified our code to use a specific user agent string or parse it from a file that has a list of different user agent strings. Please refer to our Github repository for full description of different parameters that could be used.

@@

Setup environment where this experiment was executed:
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item OS: Ubuntu 14.01 Server
  \item Duration: From April 28$^{th}$ 2030-2300 (3hr, 30min)
  \item Public IP: 172.31.20.23
  \item User agent: 526 different user agents
  \item 150-200 views every hour
\end{itemize}

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count quickly generated to 301 in few hours but unchanged as of May 3rd, 2015.
  \item User agent information can easily be changed, thus there is probably no mechanism to verify if user agent string actually matches the source OS/browser used.
  \item For user agents with BlackBerry strings, YouTube sent pure HTML files with link to RTSP stream protocol instead of adobe flash player.
\end{itemize}

@@

Here we used multiple public IP addresses with our code to pass the 301 view threshold on video hosted by YouTube. Considering only IPv4, there are little less than 4 billion public IP addresses available in the world.

@@

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count quickly generated to 301 within one hour but unchanged as of May 4$^{th}$ 2015.
  \item 5 public IP addresses isn’t enough to pass 301 view count.
\end{itemize}

@@

The Onion Router provides user anonymity on the Internet through encryption and using 3 random node connections between the source and the destination~\cite{c14}.

We thought about using TOR because it can incorporate many public IP addresses using different TOR exit nodes with our code. If the TOR daemon is configured to setup a new circuit every time our code views a YouTube video, we can use hundreds of different IP addresses since there are around 1000 different exit nodes available~\cite{c15}.

@@

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count is still stuck at 301.
  \item Source IP is visible via flash browser plugin~\cite{c14}. This means that YouTube knows where the actual request is coming from; thus, anonymity isn’t possible using TOR when viewing videos in YouTube.
\end{itemize}

@@

Virtual Private Network is a connection that extends to another network through public network connection~\cite{c23}. Many higher institutions offer VPN service so students and staff can connect to the institution’s network from home or other geographic locations.

There are many free VPN connections available and hence many users use VPN for security and privacy~\cite{c24}. Since many users use popular VPN services, we assume that YouTube knows the VPN public IPs and think multiple users can be associated with one VPN IP address. We tested this hypostasis with our code and see if it can break the 301 view count on YouTube videos.

@@

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count is still stuck at 301.
  \item Using popular VPN connection doesn’t matter.
\end{itemize}

@@

We were able to generate 301 view count on videos hosted by YouTube using our code in various different ways. However, we were not able to pass the 301 view count as of May 4$^{th}$ 2015. We also like to mention that we used combination of our experiments on one video hosted by YouTube. For example, we used VPN connection and 5 Cloud instances using multiple user agents. The result was similar as we were able to generate view count up to 301 views but no more.

Lastly, YouTube counting system isn’t perfect as it proven to allow both false positive and false negative view counts in our research. We were able to prove it allows false positive view counts by using the 4 services mentioned in section 2 \& 3. Moreover, for the videos that were stuck on 301+ views, we view the same videos manually and see if the view count will go over 301. The view counts didn’t change even after we manually view the videos; therefore, we assume that YouTube’s counting
system is also vulnerable to false negative view counts.
